An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-10-27 neurips-19/poly-embed.tex
paper tweaks

\raf{I am not sure this is the place to clarify these connections.  I added a forward reference to \S~\ref{sec:links-embeddings} at the top of this section, saying we'll move to the $\X\times\Y$ setting then, and I wonder if that's all we need to do.  If we want to do more, I think \S~\ref{sec:links-embeddings} would be the place to do it.  E.g.\ we can discuss $\Gamma(\Pr[Y\mid X=x])$ and $\gamma$, etc., using the notation at the end of \S~\ref{sec:property-elicitation}.  Jessie, feel free to give it a shot.}
\jessie{I think the forward reference is enough.  We told a reviewer we would clarify what reports are, but that also might be as simple as clarifying report = prediction.}
\proposedadd{When we discuss \emph{reports}, we are talking about the prediction yielded by $h(x)$ for the learned hypothesis function $h : \X \to \R$ over the input space $\X$.  In this case, we can think of $p$ as the conditional probability $p = Pr[Y = y | X = x]$ when the true distribution is over $\X \times\Y$.  Throughout, we abstract away the input $X \sim \X$ and can work with these conditional probabilities $p \in \simplex$.}
Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, \proposedadd{; that is, $\Gamma(p)$ is the prediction that minimizes expected loss when the outcome $Y \sim p$.  Moreover, \ldots} and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

\jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
\proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.  Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
\begin{align*}
\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
\end{align*}
The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
\begin{equation}
\ell^{top-k}(r,y) = \begin{cases}
0 & r_y = \bar r_{-y} + 1\\
\bar r - \frac 1 k & r_y = 1\\
1 + \bar r & r_y = 0
\end{cases}~,~
\end{equation}
where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Directions} \label{sec:conclusion}
% \paragraph{Summary.}
This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses.
We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.\bo{commented stuff for space}
\raf{Is this in response to some reviewer, or just because we had to comment stuff for space?}
\jessie{What we had commented for space}
\proposedadd{We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.}

>>>>

% \raf{I am not sure this is the place to clarify these connections.  I added a forward reference to \S~\ref{sec:links-embeddings} at the top of this section, saying we'll move to the $\X\times\Y$ setting then, and I wonder if that's all we need to do.  If we want to do more, I think \S~\ref{sec:links-embeddings} would be the place to do it.  E.g.\ we can discuss $\Gamma(\Pr[Y\mid X=x])$ and $\gamma$, etc., using the notation at the end of \S~\ref{sec:property-elicitation}.  Jessie, feel free to give it a shot.}
% \jessie{I think the forward reference is enough.  We told a reviewer we would clarify what reports are, but that also might be as simple as clarifying report = prediction.}
% \proposedadd{When we discuss \emph{reports}, we are talking about the prediction yielded by $h(x)$ for the learned hypothesis function $h : \X \to \R$ over the input space $\X$.  In this case, we can think of $p$ as the conditional probability $p = Pr[Y = y | X = x]$ when the true distribution is over $\X \times\Y$.  Throughout, we abstract away the input $X \sim \X$ and can work with these conditional probabilities $p \in \simplex$.}
Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

% \jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
% \proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.  Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
% \begin{align*}
% \R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
% \end{align*}
% The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
% \begin{equation}
% \ell^{top-k}(r,y) = \begin{cases}
% 0 & r_y = \bar r_{-y} + 1\\
% \bar r - \frac 1 k & r_y = 1\\
% 1 + \bar r & r_y = 0
% \end{cases}~,~
% \end{equation}
% where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
% }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Directions} \label{sec:conclusion}
% \paragraph{Summary.}
This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses (Theorem~\ref{thm:eps-thick-calibrated}).
We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.
In particular, our link construction recovers the link function proposed by~\citet{ramaswamy2018consistent} for abstain loss, as well as another simpler link based on the $L_1$ norm.
